Title

### 2024-05-06 paper/main.tex
Updates

Both in the cases when the DAG is an output of an algorithm or when constructed
by hand, it is vital to test these models against data before using them for
making any inference. In the field of Structural Equation Models (SEMs)
modification indices have been used to do this. However, as modification index
is an evaluation of the global fit of the model. An alternative is local fit of
models using CI tests where the implied conditional independences of the model
can be tested using statistical tests. Similar to modification indices, these
tests can then be used to modify our models. Figure shows an example of this
testing.

@@

One of the limitations here is there are no effect size measures available for mixed data.

@@

\subsection{Continuous Variables}
Correlation coefficient and partial correlation coefficient.

\subsection{Discrete Variables}
Chi-Squared and Cram\'er's V

\subsection{Ordinal and Continuous Variables}
Polyserial Correlation

\subsection{Ordinal Variables}
Polychoric Correlation

\subsection{Mixed data}
Background on CI tests for mixed data; but no effect size measure.

\section{Effect size for mixed data}

>>>>

Both in the cases when the DAG is an output of an algorithm or when constructed
by hand, it is vital to test these models against data before using them for
making any inference. In the field of Structural Equation Models (SEMs)
modification indices have been used to do this. However, as modification index
is an evaluation of the global fit of the model. An alternative is local fit of
models using CI tests where the implied conditional independences of the model
can be tested using statistical tests. Similar to modification indices, these
tests can then be used to modify our models. Figure shows an example of this
testing. We can not also only rely on the p-values, effect size can help in
deciding.

@@

As these CI based testing uses p-values and effect size measures from CI tests
for testing. And as mixed data is common, we need both a test and effect size
measure for mixed data. Recently, a few CI tests for mixed data have been
proposed but an effect size is still missing.

@@

We need to do both conditional and non-conditional tests. We would assume that
we are testing the statement $ X \ci Y \rvert \bm{Z} $, where $ \bm{Z} $ is a
set of conditional variables possibly null.

\subsection{Effect Size Measures}

\subsubsection{Continuous Variables}
In the case when $ \bm{Z} = \emptyset $, and when both $ X $ and $ Y $ are
continuous variables, Pearson's correlation coefficient based test can be used
which also gives an effect size measure. The p-value computation requires the
data to be normally distributed but other statistics can be used such as
Spearman's rank correlation, or Kendall's Tau.

In the case when $ \bm{Z} \neq \emptyset $, then partial correlations can be used.
In this case we first compute the residuals of $ X $ and $ Y $ using $ \bm{Z} $ as 
the predictor. We start by training two model $ X \sim \bm{Z} $ and $ Y \sim \bm{Z} $.
Then the residuals are computed for both as $ R_X = X - \hat{X} $ and $ R_Y = Y - \hat{Y} $.
After this we can do a normal non-conditional test on $ R_X $ and $ R_Y $.

\subsubsection{Discrete Variables}

Chi-Squared and Cram\'er's V

\subsubsection{Ordinal and Continuous Variables}
Polyserial Correlation

\subsubsection{Ordinal Variables}
Polychoric Correlation

\subsubsection{Mixed data}
Recently multiple tests for mixed data have been proposed but they do not have
an effect size measure.

\subsection{Canonical Correlations}

\section{Effect size for mixed data}
\subsection{Non-conditional Case}
\subsection{Conditional Case}
